Crowd density estimation from Wi-Fi positioning data in the Amsterdam Arena

### 2016-06-29 PaperOnSmoothing/draft-31052016.tex
subsections added, some corrections

*************from Sonja

@@

Formally, let $R$ be an arbitrary region from the stadium. Let $\{mac_1, mac_2,...mac_n\}$ be all MAC devices detected at time $t$.  Let $X_i$ be a random variable defined by

@@

***************end from Sonja

@@

{\it below: emphasize that we measure in a time window. The final result of stacking is not a probability density distribution but a crowd density distribution. We don't generate probabilities for number of people per bin, but we generate an estimation of number of people per bin. }\\

@@

****************begin from Sonja

@@

@@

Thus, when estimating crowd density, we ignore the MAC devices that have a randomized address and at the end we multiply the crowd density by 1.0225, to account for the ignored MAC devices. We choose factor 1.225 to allow for a safety margin: in the peaks of the graph in Fig. \ref{fig:randomized} the values are 0.225, and we would rather overestimate than underestimate the crowd density. 
Note that this ratio should be re-computed periodically, to account for the changing conditions at the smart phones market.

@@

\subsection{Validation}

>>>>

\subsubsection{Issue 1: creating a statistical ensemble}
*************from Sonja

@@

Formally, 
let $\{mac_1, mac_2,...mac_n\}$ be all MAC devices detected at time $t$. Let $R$ be an arbitrary region from the stadium.  Let $X_i$ be a random variable defined by

@@

**** below: in the kernel function there is a typo:  the negative sign in front of $u^2$ is forgotten
***************end from Sonja

@@

@@

\subsubsection{Issue 2: Conservation of mass }
****************begin from Sonja

@@

\subsubsection{Issue 3: using Big data again}

@@

Thus, when estimating crowd density, we ignore the MAC devices that have a randomized address and at the end we multiply the crowd density by 1.225, to account for the ignored MAC devices. We choose factor 1.225 to allow for a safety margin: in the peaks of the graph in Fig. \ref{fig:randomized} the values are 0.225, and we would rather overestimate than underestimate the crowd density. 
Note that this ratio should be re-computed periodically, to account for the changing conditions at the smart phones market.

@@

\subsection{Validation}
Maybe with crowd sourcing images and videos from Sensation 2015 Amsterdam White
